cvx-flats

### 2020-05-19 neurips-20/cvx-flats-statements.tex
Reorganized structure

\section{Related work}\label{sec:related-work}

@@

\begin{definition}[Consistent: loss]
	Let $\{f_m : \X \to \R\}$ be a sequence of hypothesis functions.
	A loss and link $(L,\psi)$ are consistent with respect to an original loss $\ell$ if, for all distributions $D$ over input and label spaces $\X \times\Y$, 
	\begin{align*}
	\E_D L(f_m(X), Y) \to \inf_f \E_D L(f(X), Y) &\implies \E_D \ell((\psi \circ f_m)(X), Y) \to \inf_f \E_D \ell((\psi \circ f)(X), Y)~.~
	\end{align*}
\end{definition}

%\raf{Issues with the definition:
%\begin{enumerate}
%\item Good to clarify $d:\R\times\R\to\reals_+$ -- done
%\item We have two $d$'s so we'll need a new letter... -- changed to $\mu$
%\item $D_X$ is not defined, but I got it -- clarified it was the marginal distribution
%\item You can't take an expectation over $\R$ values (not necessarily a subset of a vector space) and want the expectation over $X$ on the outside
%\end{enumerate}
%At this point I lost the thread. It looks like you're missing the hypothesis function, and $\Gamma(D)$ doesn't seem to type check -- but perhaps $\Gamma(D)$ was meant to depend on $X$ and be the hypothesis? -- and the implication also seems backwards.}
\begin{definition}[Consistent: property]
	Suppose we are given a loss $L : \R \times \Y \to \reals$ and link $\psi : \R \to \R'$.
	$(L, \psi)$ is \emph{$\mu$-consistent with respect to a property} $\gamma: \simplex \toto \R'$ for a function $\mu^\gamma:\R' \times \simplex \to \reals_+$ with $\mu^\gamma(r,p) = 0 \iff r \in \gamma(p)$, if for all $D$ over $\X \times \Y$ with marginal distributions $D_x$, and sequences $\{f_m: \X \to \R\}$, 
	\begin{equation}
	\E_{D} L(f_m(X), Y) \to \inf_f \E_{D} L( f(X), Y) \implies \E_X \mu^\gamma(\psi \circ f_m(X), D_X) \to 0~.~
	\end{equation}

@@

\begin{definition}[Calibrated]\label{def:calibrated-general}
	A loss $L:\reals^d \times \Y \to \reals$ is \emph{calibrated} with respect to a loss $\ell : \R \times \Y \to \reals$ eliciting the property $\gamma$ if there is a link $\psi : \reals^d \to \R$ such that, for all distributions $p \in \simplex$, there exists a function $\zeta : \reals_+ \to \reals_+$ with $\zeta$ continuous at $0^+$ and $\zeta(0) = 0$ such that for all $u \in \reals^d$, we have
	\begin{equation}\label{eq:calibrated-general}
	\ell( \psi(u); p) - \risk{\ell}(p)  \leq \zeta \left(  L(u;p) - \risk{L}(p) \right)~.~
	\end{equation}
\end{definition}
\begin{definition}[Calibrated: Finite predictions]\label{def:calibrated-finite}
	Let $\ell : \R \times \Y \to \reals_+$ be a discrete loss eliciting the property $\gamma$.
	A surrogate loss $L : \reals^d \times \Y \to \reals_+$  and link $\psi:\reals^d \to \R$ pair $(L, \psi)$ is \emph{calibrated} with respect to $\ell$ if 
	\begin{equation}\label{eq:calibration}
	\forall p \in \simplex: \inf_{u \in \reals^d : \psi(u) \not \in \gamma(p)} L(u;p) > \inf_{u \in \reals^d} L(u;p)~.~
	\end{equation}
\end{definition}

@@

	Now consider the data distribution $D$ that has a point mass on some $x \in \X$, where $p = D_x$.
	Moreover, let $f_m$ be any sequence of functions with $f_m(x) = u_m$ for all $m$.
	We then have $L(f_m(x); p) = L(u_m; p) \to \risk{L}(p)$, so $\lim_{m \to \infty}\zeta(L(u_m;p) - \risk{L}(p)) \to 0$.
	This gives $\ell(\psi(u_m);p) > \risk{\ell}(p) + \epsilon_m$ for all $m$, and $\epsilon_m \to 0$.
	We can now observe that we do not have consistency as $\ell(\psi(u_m); p) \not \to \risk{\ell}(p)$.
	Therefore, if $(L, \psi)$ are consistent with respect to $\ell$, they are also calibrated with respect to $\ell$.

%commented out May 14, 2020 to adapt Hari/Shivani's proof
%Since consistency must hold for all $D$ over $\X \times \Y$, let us focus on distributions $D$ such that the probability of any $x \in \X$ is a point mass.
%If consistency implies calibration for the marginal distributions $D_x$ for all $x \in \X$, then it holds for all $D$.
%Now, for such distributions, we have 
%\begin{align*}
%\E_{D_x} L(f_m(x), Y) \to \inf_f \E_{D_x} L(f(x), Y) &\implies \E_{D_x} \ell((\psi \circ f_m)(x), Y) \to \inf_f \E_{D_x} \ell((\psi \circ f)(x), Y)~,~
%\end{align*}
%for all $x \in \X.$
%This allows us to focus on $p \in \simplex$, abstracting away hypothesis classes to consider general predictions $u$.
%
%Now, fix $p \in \simplex$.
%We proceed in two cases; first, when we approach the optimal loss, then when we do not. 
%If $L(u;p) \to \inf_{u'} L(u';p)$, then $\ell(\psi(u); p) \to \inf_{r}\ell(r; p)$.
%Substituting into~\eqref{eq:calibrated-general}, we see the bound is satisfied by any function $\zeta$ satisfying calibration requirements; namely, $\zeta(0) = 0$ and continuity at $0$.
%%%adapting tewari proof
%%%Suppose $(L, \psi)$ is calibrated with respect to $\ell$ but there exists $\epsilon > 0$ and seequence $\{p_m\}$ such that $\ell(\psi(u_m); p_m) \leq \inf_r\ell(r;p_m) - \epsilon$ and $\left(L(u_m;p_m) - \inf_{u'}L(u'; p_m)\right) \to 0$.
%%%Since $\{p_m\}$ comes from a compact set, there is a convergent subsequence that limits to $p$.
%%%As $\risk{L}$ is continuous over $\simplex$, we get $L(u_m; p_m) \to \inf_{u'} L(u'; p)$.
%
%\jessie{I'm not 100\% sure this is the \emph{only} case... this is what isn't covered by Tewari's proof~\cite[Appendix A; pf of thm 2]{tewari2007consistency}}
%Now if $L(u;p) \not \to \inf_{u'}L(u; p)$, we do not know anything about the convergence of $\ell$.
%However, if there was distribution $p \in \simplex$ such that $\ell(\psi(u); p) - \inf_r \ell(r;p) > \zeta(L(u;p) - \inf_{u'} L(u';p))$ for all strictly increasing functions $\zeta$, it must be because there exists a $u'$ so that $L(u';p) > L(u;p), \ell(\psi(u); p) = \infty$, and $\ell(\psi(u'); p) < \infty$.
%However, we cannot have $\ell(\psi(u); p) = \infty$ unless $\ell$ was allowed to take on infinite values, which we do not allow in the definition of $\ell$.
\end{proof}

@@

\subsection{On dimensionality of consistent convex surrogates}
\begin{definition}[Flat]
	A \emph{flat} $F$ of $\reals^n$ is an affine subspace of $\reals^n$.
	In other words, $F\subseteq \reals^n$ can be written $F=\{x\in\reals^n : Wx + b = 0\}$ for some $W\in\reals^{d\times n}$ and $b\in\reals^d$ where $d\leq n$.
	The dimension of the flat $F$ is given by $f := n - \mathrm{rank}(W)$.
\end{definition}

@@

\newpage
\appendix
\section{Omitted proofs}
\begin{enumerate}
	\item [A] $\zeta:\reals \to \reals_+$ satisfies $\zeta : 0 \mapsto 0$ and is continuous at $0$.
	\item [B] $\epsilon_m \to 0 \implies \zeta(\epsilon_m) \to 0$.
	\item [C] For all $u \in \reals^d$, $R_\ell(\psi(u); p) \leq \zeta(R_L(u;p))$.
	\item [D] For all $p \in \simplex$ and sequences $\{u_m\}$ so that $R_L(u_m; p) \to 0$, we have $R_\ell(\psi(u_m); p) \to 0$.
\end{enumerate}

@@

\begin{lemma}\label{lem:calib-converging-regrets}
	A surrogate and link $(L,\psi)$ are calibrated (via definition~\ref{def:calibrated-general}) with respect to $\ell$ if and only if, for all $p \in \simplex$ and sequences $\{u_m\}$ so that $R_L(u_m; p) \to 0$, we have $R_\ell(\psi(u_m); p) \to 0$.
\end{lemma}
\begin{proof}
	$\implies$ Take a sequence $\{u_m\}$ so that $R_L(u_m;p) \to 0$.
	Since $\zeta(0) = 0$ and $\zeta$ is continuous at $0$, $\zeta(R_L(u_m;p)) \to 0$ by calibration.
	As regret is nonnegative, we then have $R_\ell(\psi(u_m); p) \to 0$

	$\impliedby$ Consider $\zeta(c) := \inf_{u: R_L(u;p) \geq c} R_\ell(\psi(u); p)$.for nonnegative values of $c$, and $\zeta(c) = 0$ for $c < 0$.
	We will show $R_L(u_m; p) \to 0 \implies R_\ell(\psi(u_m); p) \to 0$ gives calibration via the function $\zeta$ constructed above.

	\jessie{Outline: 1. $\zeta$ satisfies requirements (A).  2. Verify bound is true as approach $0$ by assumption on regrets. 3. Verify bound is true elsewhere by construction of $\zeta$.}

	First, we can verify that $\zeta$ as constructed maps is continuous at $0$ and $\zeta(0) = 0$.
	\jessie{continuous: TODO}
	As $\risk{L}$ and $\risk{\ell}$ are well-defined for all $p \in \simplex$, taking $u = \Gamma(p)$ yields $\zeta(0) = \inf_u (R_\ell(\psi(u); p))$, which is $0$ as long as there is some $u$ so that $\psi(u) = \gamma(p)$ for each $p \in \simplex$.

@@

	Last, we observe that the bound in Equation~\eqref{eq:calibrated-general} is satisfied for $\{u_m\} \not \to 0$ by construction of $\zeta$.	
	\jessie{TODO}
\end{proof}

>>>>

\section{Background and Related work}\label{sec:related-work}

\begin{definition}[Calibrated: Finite predictions]\label{def:calibrated-finite}
	Let $\ell : \R \times \Y \to \reals_+$ be a discrete loss eliciting the property $\gamma$.
	A surrogate loss $L : \reals^d \times \Y \to \reals_+$  and link $\psi:\reals^d \to \R$ pair $(L, \psi)$ is \emph{calibrated} with respect to $\ell$ if 
	\begin{equation}\label{eq:calibration}
	\forall p \in \simplex: \inf_{u \in \reals^d : \psi(u) \not \in \gamma(p)} L(u;p) > \inf_{u \in \reals^d} L(u;p)~.~
	\end{equation}
\end{definition}

@@

\section{Consistency implies indirect elicitation}\label{sec:consis-implies-indir}
\begin{definition}[Consistent: loss]
	Let $\{f_m : \X \to \R\}$ be a sequence of hypothesis functions.
	A loss and link $(L,\psi)$ are consistent with respect to an original loss $\ell$ if, for all distributions $D$ over input and label spaces $\X \times\Y$, 
	\begin{align*}
	\E_D L(f_m(X), Y) \to \inf_f \E_D L(f(X), Y) &\implies \E_D \ell((\psi \circ f_m)(X), Y) \to \inf_f \E_D \ell((\psi \circ f)(X), Y)~.~
	\end{align*}
\end{definition}

\begin{definition}[Consistent: property]
	Suppose we are given a loss $L : \R \times \Y \to \reals$ and link $\psi : \R \to \R'$.
	$(L, \psi)$ is \emph{$\mu$-consistent with respect to a property} $\gamma: \simplex \toto \R'$ for a function $\mu^\gamma:\R' \times \simplex \to \reals_+$ with $\mu^\gamma(r,p) = 0 \iff r \in \gamma(p)$, if for all $D$ over $\X \times \Y$ with marginal distributions $D_x$, and sequences $\{f_m: \X \to \R\}$, 
	\begin{equation}
	\E_{D} L(f_m(X), Y) \to \inf_f \E_{D} L( f(X), Y) \implies \E_X \mu^\gamma(\psi \circ f_m(X), D_X) \to 0~.~
	\end{equation}

@@

@@

	Now consider the data distribution $D$ that has a point mass on some $x \in \X$, where $p = D_x$.
	Moreover, let $f_m$ be any sequence of functions with $f_m(x) = u_m$ for all $m$.
	We then have $L(f_m(x); p) = L(u_m; p) \to \risk{L}(p)$, so $\lim_{m \to \infty}\zeta(L(u_m;p) - \risk{L}(p)) \to 0$.
	This gives $\ell(\psi(u_m);p) > \risk{\ell}(p) + \epsilon_m$ for all $m$, and $\epsilon_m \to 0$.
	We can now observe that we do not have consistency as $\ell(\psi(u_m); p) \not \to \risk{\ell}(p)$.
	Therefore, if $(L, \psi)$ are consistent with respect to $\ell$, they are also calibrated with respect to $\ell$.
\end{proof}

@@

\begin{definition}[Flat]
	A \emph{flat} $F$ of $\reals^n$ is an affine subspace of $\reals^n$.
	In other words, $F\subseteq \reals^n$ can be written $F=\{x\in\reals^n : Wx + b = 0\}$ for some $W\in\reals^{d\times n}$ and $b\in\reals^d$ where $d\leq n$.
	The dimension of the flat $F$ is given by $f := n - \mathrm{rank}(W)$.
\end{definition}

@@

\newpage
\appendix
\section{A general notion of calibration}

\begin{definition}[Calibrated]\label{def:calibrated-general}
	A loss $L:\reals^d \times \Y \to \reals$ is \emph{calibrated} with respect to a loss $\ell : \R \times \Y \to \reals$ eliciting the property $\gamma$ if there is a link $\psi : \reals^d \to \R$ such that, for all distributions $p \in \simplex$, there exists a function $\zeta : \reals_+ \to \reals_+$ with $\zeta$ continuous at $0^+$ and $\zeta(0) = 0$ such that for all $u \in \reals^d$, we have
	\begin{equation}\label{eq:calibrated-general}
	\ell( \psi(u); p) - \risk{\ell}(p)  \leq \zeta \left(  L(u;p) - \risk{L}(p) \right)~.~
	\end{equation}
\end{definition}

Consider the following four conditions:
\begin{enumerate}
	\item [A] $\zeta:\reals \to \reals_+$ satisfies $\zeta : 0 \mapsto 0$ and is continuous at $0$.
	\item [B] $\epsilon_m \to 0 \implies \zeta(\epsilon_m) \to 0$.
	\item [C] For all $u \in \reals^d$, $R_\ell(\psi(u); p) \leq \zeta(R_L(u;p))$.
	\item [D] For all $p \in \simplex$ and sequences $\{u_m\}$ so that $R_L(u_m; p) \to 0$, we have $R_\ell(\psi(u_m); p) \to 0$.
\end{enumerate}

@@

\begin{lemma}\label{lem:calib-converging-regrets}
	A continuous surrogate and link $(L,\psi)$ are calibrated (via definition~\ref{def:calibrated-general}) with respect to $\ell$ if and only if, for all $p \in \simplex$ and sequences $\{u_m\}$ so that $R_L(u_m; p) \to 0$, we have $R_\ell(\psi(u_m); p) \to 0$.
\end{lemma}
\begin{proof}
	$\implies$ Take a sequence $\{u_m\}$ so that $R_L(u_m;p) \to 0$.
	Since $\zeta(0) = 0$ and $\zeta$ is continuous at $0$, $\zeta(R_L(u_m;p)) \to 0$ by calibration.
	As regret is nonnegative, we then have $R_\ell(\psi(u_m); p) \to 0$

	$\impliedby$ Consider $\zeta(c) := \sup_{u: R_L(u;p) \leq c} R_\ell(\psi(u); p)$.for nonnegative values of $c$, and $\zeta(c) = 0$ for $c < 0$.
	We will show $R_L(u_m; p) \to 0 \implies R_\ell(\psi(u_m); p) \to 0$ gives calibration via the function $\zeta$ constructed above.

	\jessie{Outline: 1. $\zeta$ satisfies requirements (A).  2. Verify bound is true elsewhere by construction of $\zeta$.}

	First, we can verify that $\zeta$ as constructed is continuous at $0$ and $\zeta(0) = 0$.
	As $c < 0 \implies \lim_{c \to 0^-} \zeta(c) = 0$, we need to show first that $\lim_{c \to 0^+} \zeta(c) = 0$ and $\zeta(0) = 0$.
	Consider $\{u_m\}$ so that $R_L(u_m;p) \to 0$. Since $R_\ell(\psi(u_m); p) \to 0$, we have the supremum of a function continuous (at $0^+$) is also continuous at $0^+$, so we have $\lim_{c \to 0^+} \zeta(c) = 0$.

	As $\risk{L}$ and $\risk{\ell}$ are well-defined for all $p \in \simplex$, taking any $\{u_m\} \to u \in \Gamma(p)$ yields $\zeta(0) = \sup_{u':R_L(u;p) = 0} (R_\ell(\psi(u'); p)) = \lim_{m \to \infty} R_\ell(\psi(u_m); p) = 0$, with equality following since $\{u_m\}$ is arbitrary. \jessie{Not super happy with this, but I also think I'm making it more complicated than it needs to be.}

@@

	Last, we observe that the bound in Equation~\eqref{eq:calibrated-general} is satisfied for $\{u_m\} \not \to 0$ by construction of $\zeta$.

	Suppose $R_\ell(\psi(u);p) = c$.
	For all $u \in \reals^d$, calibration via $\zeta$ yields $R_\ell(\psi(u);p) \leq \sup_{u' : R_L(u';p) \leq R_L(u,p)} R_\ell(\psi(u') ; p)$.
	As $u$ is in the space of the supremum ($R_L(u;p) \leq R_L(u;p)$), we then have calibration by definition of the supremum.
\end{proof}
